---
title: "p8105_hw5_bf2506"
author: "bf2506"
date: "2022-11-15"
output: github_document
---
```{r load package, message=FALSE, warning=FALSE}
library(tidyverse)
```

### Problem 2

```{r read homi_data}
homi_data = 
  read.csv("./data/homicide-data.csv") %>%
  janitor::clean_names()
```
**Describe the raw data:**

* The dataset has `r ncol(homi_data)` variables and `r nrow(homi_data)` observations.

  * "uid"(the abbreviation of city - number); "reported_date"
  
  * "victim_last"(last name of victim); "victim_first"(first name of victim); "victim_race"; "victim_age"; "victim_sex"
  
  * "city"; "state"; "lat"(latitude); "lon"(longitude); 
  
  * "disposition": 
    * Closed by arrest when *police reported that to be the case*
    * Closed without arrest when *police reported that to be “exceptionally cleared.”* Those are cases in which there is sufficient evidence but an arrest is not possible, for example, if the suspect has died.
    * Open/No arrest: *All other cases* were classified as having no arrest.

##### Part A

Create a city_state variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r message=FALSE, warning=FALSE}
homi_data = 
  homi_data %>% 
  mutate(city_state = paste(city, state, sep = ", ", collapse = NULL))

total_df = 
  homi_data %>% 
  group_by(city_state) %>% 
  summarize(total_number_homicide = n())

unsolved_df = 
  homi_data %>%
  filter(disposition != "Closed by arrest") %>% 
  group_by(city_state) %>% 
  summarize(number_unsolved_homicide = n())

total_unsolved_df = 
  left_join(total_df, unsolved_df) %>% 
  replace(is.na(.), 0)
```
*Tulsa, AL doesn't have a unsolved homicide, so it is not included in unsolved_df.*

##### Part B

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r message=FALSE, warning=FALSE}
balt_prop = 
  prop.test(1825, 2827, p = NULL, 
            alternative = "two.sided", conf.level = 0.95, correct = TRUE)
balt_prop

balt_prop_tibble = broom::tidy(balt_prop)
balt_prop_tibble

balt_prop_tibble %>% pull(estimate)
balt_prop_tibble %>% pull(conf.low)
balt_prop_tibble %>% pull(conf.high)
balt_prop_tibble %>% mutate(ci = paste("(", round(conf.low, 4), ",", round(conf.high, 4), ")")) %>% pull(ci)
```

##### Part C

Run prop.test for every city. Extract *the proportion of unsolved homicides* and *the confidence interval*. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r message=FALSE, warning=FALSE}
prop_df = 
  total_unsolved_df %>% 
  mutate(result = purrr::map2(.x = number_unsolved_homicide, .y = total_number_homicide, ~broom::tidy(prop.test(x = .x, n = .y, alternative = "two.sided", conf.level = 0.95, correct = TRUE)))) %>% 
  unnest(result) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(confidence_interval = paste("(", round(conf.low, 4), ",", round(conf.high, 4), ")"))

prop_df
```
Considering the total number of homicides is 1 and the number of unsolved homicides is 0 in Tulsa, AL, the data is too small and insufficient in prop.test. We should pay attention to Tulsa, AL data.

##### Part C

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides
```{r}
Estimates_CIs_Plot = 
  prop_df %>% 
  filter(city_state != "Tulsa, AL") %>% 
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Estimate And CI Of Proportion Of Unsolved Homicides For Each City", x = "City, State", y = "Estimate / CI")

Estimates_CIs_Plot
```
Since I discussed aboved, the  total number of homicides and the number of unsolved homicides in Tulsa, AL are not sufficient and enough to analyze and run a prop.test, I drop this data when making the "Estimate And CI Of Proportion Of Unsolved Homicides For Each City" plot.

### Problem 3

