---
title: "p8105_hw5_bf2506"
author: "bf2506"
date: "2022-11-15"
output: github_document
---
```{r load package, message=FALSE, warning=FALSE}
library(tidyverse)
```

### Problem 2

```{r read homi_data}
homi_data = 
  read.csv("./data/homicide-data.csv") %>%
  janitor::clean_names()
```
**Describe the raw data:**

* The dataset has `r ncol(homi_data)` variables and `r nrow(homi_data)` observations.

  * "uid"(the abbreviation of city - number); "reported_date"
  
  * "victim_last"(last name of victim); "victim_first"(first name of victim); "victim_race"; "victim_age"; "victim_sex"
  
  * "city"; "state"; "lat"(latitude); "lon"(longitude); 
  
  * "disposition": 
    * Closed by arrest when *police reported that to be the case*
    * Closed without arrest when *police reported that to be “exceptionally cleared.”* Those are cases in which there is sufficient evidence but an arrest is not possible, for example, if the suspect has died.
    * Open/No arrest: *All other cases* were classified as having no arrest.

Then, create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
homi_data = 
  homi_data %>% 
  mutate(city_state = paste(city, state, sep = ",", collapse = NULL))
```

